Data Preparation, Integration and Cleaning

### 2018-05-29 scripts/3_data_prep.Rmd
Set data_prep eval to FALSE
Update data prep to relative paths

---
title: "Data Preparation, Integration and Cleaning"
output:
  pdf_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
#knitr::opts_chunk$set(eval=TRUE)
```

@@

This file details the initial data preparation and cleaning that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).  Both datasets have had some initial pre-processing done, the details of which are found in **1_str_preprocess.R** and **2_ltr_preprocess.R**.

@@

  library(tidyverse)
  library(sf)
  library(geosphere)
  library(ggmap)
  library(multidplyr)
  library(tmap)

@@

Then we set the paths to the data

```{r set_paths, message=FALSE, warning=FALSE, comment=FALSE, echo=TRUE, results='hide'}

  data_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'data')
  code_path <- file.path('c:', 'code', 'research', 'airbnbmelbourne')
  fig_path <- file.path('c:', 'dropbox', 'research', 'airBNB', 'figures')

@@

  source(file.path(code_path, 'functions', 'abb_Functions.R'))

@@

 # Set specific colors
  str_col <- col_df$rgb[1]
  ltr_col <- col_df$rgb[3]
  sm_col <- col_df$rgb[c(2, 4, 5, 8, 6)]

@@

Next we load in the raw data.  The short-term rental (Airbnb) data is found in two separate files, one providing information on the property itself and one providing a daily record of bookings.

```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE, cache=FALSE, echo=TRUE}

  str_tdf <- readRDS(file.path(data_path, 'prepared', 'str_data.RDS'))

  ltr_tdf <- readRDS(file.path(data_path, 'prepared', 'ltr_data.RDS'))

@@

And, finally, we load three GIS shapefiles.  The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area. We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]

@@

  suburb_sf <- sf::st_read(file.path(data_path, 'geographic', 'melbSuburbs.shp')) %>%
    st_transform(crs=4283)
  sa1_sf <- sf::st_read(file.path(data_path, 'geographic', 'sa1s.shp')) %>%
    st_transform(crs=4283)
  beach_sf <- sf::st_read(file.path(data_path, 'geographic','portPhillipBeach.shp')) %>%
    st_transform(crs=4283)

@@

Next we filter the observations by time.  Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.  To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.  Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).  In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.  Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.  While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.

@@

1. **House**:  Includes properties labeled 'House' or 'Townhouse'
2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
3. **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse', Villa' and 'Yurt.

@@

1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace' or 'Townhouse'
2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
3. **Other**: Includes properties labeled as 'Semi' and 'Villa'

@@

In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.  In other words, it is very common in the industry (and when looking for a short term ltral) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.  As a result we examine the combinations of the two.

@@

 ## Build the map object

@@

  plot(studyarea_sf)

@@

Finally we add the spatial data back onto the tabular data and filtering out those outside of the study area using an inner join. We then have to remove the geometry field as it causes issues with future analyses (for now)

@@

Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year (Figure 10).  Short term revenues range from neglible to highs of greater than \$80,000.  While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not. Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, clean_count, core_suburbs,
        file=paste0(data_path, '/prepared/prepared_data.RData'))

>>>>

---
title: "Data Preparation, Integration and Cleaning"
output:
  htlm_document: default
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}

  knitr::opts_chunk$set(echo = TRUE, eval=FALSE)

@@

This file details the initial data preparation and cleaning that we have applied to the AirBNB nightly data from www.AirDNA.co as well as to the long-term rental data from Australia Property Monitors (APM).  Both datasets have had some initial pre-processing done, the details of which are found in **1_str_preprocessing.RMD** and **2_ltr_preprocessing.RMD**.

@@

  library(tidyverse)
  library(sf)
  library(multidplyr) # Note you have to install from the github site hadley/multidplyr
  library(tmap)

```{r saf}

@@

@@

  source(file.path(getwd(), 'functions', 'abb_Functions.R'))

@@

 # Set specific colors
  str_col <- col_df$rgb[1]
  ltr_col <- col_df$rgb[3]
  sm_cols <- col_df$rgb[c(2, 4, 5, 8, 6)]

@@

Next we load in the raw data from the previous pre-processing activities.

```{r load_str_data, message=FALSE, warning=FALSE, comment=FALSE}

  str_tdf <- readRDS(file.path(getwd(), 'data', 'prepared', 'str_data.RDS'))

  ltr_tdf <- readRDS(file.path(getwd(), 'data', 'prepared', 'ltr_data.RDS'))

@@

Then we load three GIS shapefiles.  The first two denote suburb and Statistical Area 1 (sa1) boundaries in the Melbourne area. We also load a shapefile that contains the location of the beach areas along Port Phillip Bay.^[Only those east of the mouth of Yarra River as those to the west are primarily industrial land.]

@@

  suburb_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic', 'melbSuburbs.shp')) %>%
    st_transform(crs=4283)
  sa1_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic', 'sa1s.shp')) %>%
    st_transform(crs=4283)
  beach_sf <- sf::st_read(file.path(getwd(), 'data', 'geographic','portPhillipBeach.shp')) %>%
    st_transform(crs=4283)

@@

We begin by filtering the observations by time.  Our hypothetical simulated decision is that of an investor who purchases a property on September 1, 2015 and must decide on traditional long term rental versus an AirBNB, short term rental approach to generating income.  To determine the likely long term rental rate for any given property, we will use the observed rental transactions from the market from September 1, 2014 to August 31, 2015.  Taking the AirBNB approach allows the owner to change rates over time and is subjected to daily changes in the market (supply and demand factors).  In this simulated example we will use AirBnB data from September 1, 2015 to August 31, 2016 to represent the actual AirBNB market conditions over the time period in question.  Another reason for using these two period of data is that the AirBNB data has missing daily values prior to September 1, 2015.  While we have imputed these missing daily observations, we hold the actual observed values to be of greater accuracy and have designed the initial simulated example to take advantage of the full observed set.

@@

1. **House**:  Includes properties labeled 'House', 'Townhouse' or 'Villa'
2. **Apartment**: Includes properties labeled as 'Apartment' or 'Condominium'
3. **Other**: Includes properties labeled as 'Bed & Breakfast', 'Boat', 'Bungalow', 'Cabin', 'Camper/RV', 'Chalet', 'Dorm', 'Earth House', 'Hut', 'Igloo', 'Loft', 'Other', 'Tent', 'Treehouse' and 'Yurt.

@@

1. **House**:  Includes properties labeled 'Duplex', 'House', 'Terrace', 'Townhouse' or 'Villa'
2. **Apartment**: Includes properties labeled as 'Unit' or 'Studio'
3. **Other**: Includes properties labeled as 'Semi'

@@

In addition to looking at bedrooms and bathrooms as separate dimensions of properties, they can also be considered together.  In other words, it is very common in the industry (and when looking for a short term rental) to specify searches by bed/bath combination for obvious reasons -- 1 bedroom with 3 baths is inefficient and 4 bedrooms with 1 bath is uncomfortable.  As a result we examine the combinations of the two.

@@

@@

  plot(studyarea_sf$geometry)

@@

Finally we add the spatial data back onto the tabular data and filtering out those outside of the study area using an inner join. We then have to remove the geometry field as it causes issues with future analyses (for now).

@@

Looking at the distribution of the revenues from each tenure type, we see that those for the long-term rentals are for more consistent, with the vast majority totaling between \$12,000 to \$30,000 per year.  Short term revenues range from neglible to highs of greater than \$80,000.  While this simple analysis does not control for location and product differences, it does highlight the fact that some Airbnb owners are likely making greater revenues than in long-term rentals, but that most are likely not. Also, the high number of very low yield Airbnb properties also suggests that some owners may not be focused on maximizing revenue, but instead prefer the flexibility of short-term leasing.

@@

   save(str_tdf, ltr_tdf, str_sf, ltr_sf, studyarea_sf, suburb_sf, beach_sf, sa1_sf,
        col_df, clean_count, core_suburbs,
        file=paste0(file.path(getwd(), 'data', 'prepared', 'prepared_data.RData')))
